---
title: "R Notebook"
output: html_notebook
---
```{r}
x <-10
class(x)
```
```{r}
x <- 10
print(x)
```
```{r}
y<- "CSPT"
print(y)
```
```{r}
z <- 10.5
class(z)
z <- as.integer(z)
class(z)
print(z)
```

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

```{r}
plot(cars)
```
```{r}
a <- 200

b <- 33

if (b > a) {

print("b is greater than a")

} else if (a == b) {

print("a and b are equal")

} else {

print("a is greater than b")

}
```
```{r}
i <- 1
while (i < 60) {
  print(i)
  i <- i + 1
}
```
```{r}
# Vector of strings

fruits <- c("banana", "apple", "orange")

# Print fruits

fruits

# Vector with numerical values in a sequence

numbers <- 1:10

numbers
```{r}
thislist <- list("apple", "banana", "cherry")

thislist[1] <- "blackcurrant"

# Print the updated list

thislist
```
```{r}
# Create a matrix

thismatrix <- matrix(c(1,2,3,4,5,6), nrow = 3, ncol = 2)

# Print the matrix

thismatrix[1, 2]
```

Note: There are a lot more other operations in matrix#a# An array with one dimension with values ranging from 1 to 24
```{r}
# An array with one dimension with values ranging from 1 to 24

thisarray <- c(1:24)

thisarray

# An array with more than one dimension

multiarray <- array(thisarray, dim = c(4, 3, 2))

multiarray[2, 3, 2]
```
```{r}
Data_Frame <- data.frame (

Training = c("Strength", "Stamina", "Other"),

Pulse = c(100, 150, 120),

Duration = c(60, 30, 45)

)

Data_Frame[1]

Data_Frame[["Training"]]

Data_Frame$Training
```
```{r}
# Create a factor

music_genre <- factor(c("Jazz", "Rock", "Classic", "Classic", "Pop", "Jazz", "Rock",
"Jazz"))

# Print the factor

music_genre
```
```{r}
for (x in 1:10) {

print(x)

}
```
```{r}
fruits <- list("apple", "banana", "cherry")

for (x in fruits) {

if (x == "banana") {

next # continue statement

}

print(x)

}
```
```{r}
x <- c(1, 2, 3, 4, 5)

y <- c(3, 7, 8, 9, 12)

plot(x, y, main="My Graph", xlab="The x-axis", ylab="The y axis")
```
```{r}
x <- c(1, 2, 3, 4, 5)

y <- c(3, 7, 8, 9, 12)

plot(x, y, type="l", main="My Graph", xlab="The x-axis", ylab="The y axis")
```
```{r}
# Create a vector of pies

x <- c(10,20,30,40)

# Create a vector of labels

mylabel <- c("Apples", "Bananas", "Cherries", "Dates")

# Create a vector of colors

colors <- c("blue", "yellow", "green", "black")

# Display the pie chart

pie(x, label = mylabel, main = "Pie Chart", col = colors)

# Display the explanation box

legend("bottomright", mylabel, fill = colors)
```
```{r}
x <- c("A", "B", "C", "D")

y <- c(2, 4, 6, 8)

barplot(y, names.arg = x, width = c(1,2,3,4))
```
